New insights into the Weddell Sea ecosystem applying a quantitative network approach

### 2022-12-28 Manuscript/Manuscript.Rmd
Corrected minor suggestions. Still tidying Intro
Finished tidying Intro

<!-- Paragraph on unweighted and weighted networks here? -->
We should maybe write a paragraph about weighted and unweighted approaches here, where we also introduce the approach we used... 
Need to check Kortsch et al. 201

<!-- Insights of network science to polar ecosystems -->
> [susanne] I moved the paragraph below. it makes more sense to first talk about polar regions in general and then introduce the Weddell Sea. TIM: Agree.

Using a network approach, different types (e.g., terrestial, lake, marine) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022]. Some of these studies from the Arctic show how food web properties (e.g., connectance) are constrained by environmental factors such as sea ice cover and seawater temperature [@Kortsch2019; @Pecuchet2022]. In the Southern Ocean, important insights have been gained into mechanisms of energy flow, the relative importance and traits of individual species and the influence of environmental variables on the structure of local food webs [@Cordone2020; @Rossi2019].
> [susanne] what do you mean here: the relative importance and traits of individual species? What important mechanisms? Can we be more specefic? Can we also be more specific about how environmental variables (e.g., sea-ice) influence the structure of local food webs in the SO?
Need to check Rossi2019

<!-- Climate change in Weddell Sea -->
The Weddell Sea is expected to be one of the last regions of the Southern Ocean to experience the consequences of climate change due to its extensive ice cover and ocean currents [@Teschke2021] resulting in less sea surface warming compared to other areas of the Southern Ocean. Because of these environmental characteristics, the Weddell Sea may serve as a refuge for Antarctic species which depend on sea ice (e.g. krill, emperor penguin, Weddell seal) or have low heat tolerance (e.g., most notothenoid fishes) due to their adaptations to freezing temperatures [@Griffiths2017]. While essential large-scale hydrodynamic relationships are relatively well-known for this region [@deSteur2019], information on the current distribution, abundance and sensitivity to climate change is only partially known for a few species (e.g., emperor penguin) [@Houstin2022].
> [susanne]it is not clear from the text why Weddell Sea is one of the last regions of the SO to face the consequences of warming, be explicit here, how are the currents affecting the Weddell Sea?
Need to check Teschke2021

<!-- Food web studies about Weddell Sea / Key species or species role -->
Overall, the complexity the Weddell Sea food web is high and consists of 488 species and 16200 predator-prey interactions[@Jacob2011]. In an attempt to better understand species role related to food web stability, Jacob et al. (2011) performed secondary extinction experiments and found that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions. These findings highlighted the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022]. Other investigations have considered this food web though in a meta-analysis context....[more text here, WHAT DO THESE META_ANALSYES STUDIES SHOW] [@Brose2019; @Perkins2022; @Saravia2022].

@@

The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3). <!-- Gamma parameters: added in Supplementary Material -->

>>>>

<!-- Paragraph on unweighted and weighted networks here? -->
We should maybe write a paragraph about weighted and unweighted approaches here, where we also introduce the approach we used... @Susanne could you write this, please?

<!-- Insights of network science to polar ecosystems -->
> [susanne] I moved the paragraph below. it makes more sense to first talk about polar regions in general and then introduce the Weddell Sea. TIM: I agree.

Using a network approach, different types (e.g., terrestial, lake, marine) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022]. Some of these studies from the Arctic show how food web properties (e.g., connectance) are constrained by environmental factors such as sea ice cover and seawater temperature [@Kortsch2019; @Pecuchet2022]. In the Southern Ocean, important insights have been gained into mechanisms of energy flow, the relative importance and traits of individual species and the influence of environmental variables on the structure of local food webs [@Cordone2020; @Rossi2019]. For instance, in Potter Cove (West Antarctic Peninsula) the substratum type (i.e. hard/soft or rocks/sediments) plays a significant role in the structure and stability of the food web. In Terra Nova Bay (Ross Sea), the architecture of biodiversity was reshaped by the pulsed input of sympagic food sources following sea-ice break up, with food web simplification, decreased intraguild predation, potential disturbance propagation and increased vulnerability to biodiversity loss [@Rossi2019].
> [susanne] what do you mean here: the relative importance and traits of individual species? What important mechanisms? Can we be more specefic? Can we also be more specific about how environmental variables (e.g., sea-ice) influence the structure of local food webs in the SO?
TIM: I added 2 examples in this regard.

<!-- Climate change in Weddell Sea -->
The Weddell Sea is expected to be one of the last regions of the Southern Ocean to experience the consequences of climate change due to its extensive ice cover and ocean currents [@Teschke2021] resulting in less sea surface warming compared to other areas of the Southern Ocean. This Sea plays an important role in driving global thermohaline circulation and ventilating the global abyssal ocean because it generates a considerable part of the Antarctic Bottom Water [@Fahrbach2009]. The formation of those dense water masses in the Weddell Sea is facilitated by the large-scale cyclonic Weddell Gyre. Because of these environmental characteristics, the Weddell Sea may serve as a refuge for Antarctic species which depend on sea ice (e.g. krill, emperor penguin, Weddell seal) or have low heat tolerance (e.g., most notothenoid fishes) due to their adaptations to freezing temperatures [@Griffiths2017]. While essential large-scale hydrodynamic relationships are relatively well-known for this region [@deSteur2019], information on the current distribution, abundance and sensitivity to climate change is only partially known for a few species (e.g., emperor penguin) [@Houstin2022].
> [susanne]it is not clear from the text why Weddell Sea is one of the last regions of the SO to face the consequences of warming, be explicit here, how are the currents affecting the Weddell Sea?
TIM: added 2 phrases in this regard.
@LAS could you add this reference to Zotero? Fahrbach, E., Beszczynska-Möller, A., & Rohardt, G. (2009). Polar oceans-an oceanographic overview. In Biological Studies in Polar Oceans-Exploration of Life in Icy Waters, G. and H. Hempel (Eds.), Wirtschaftsverlag NW, Bremerhaven (pp. 17-36). https://epic.awi.de/id/eprint/23118/

<!-- Food web studies about Weddell Sea / Key species or species role -->
Overall, the complexity the Weddell Sea food web is high and consists of 488 species and 16200 predator-prey interactions[@Jacob2011]. In an attempt to better understand species role related to food web stability, Jacob et al. (2011) performed secondary extinction experiments and found that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions. These findings highlighted the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Perkins2022; @Saravia2022]. Other investigations have considered this food web though in a meta-analysis context, showing that high predator-prey body-mass ratios, which create weak interactions that stabilize communities against perturbations and maintain ecosystem functioning, are found for predator groups with specific trait combinations including small vertebrates and large swimming or flying predators [@Brose2019].

<!-- ....[more text here, WHAT DO THESE META_ANALSYES STUDIES SHOW] [@Brose2019; @Perkins2022; @Saravia2022]. TIM: I added specific results from Brose2019 -->

@@

The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3). <!-- Gamma parameters ?? TIM: added them in Supplementary Material. -->
